### 2017-02-07 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
Partial Scribe of 5

>>>>

%Q5
Let $G=(V,E)$ be a metric graph with edge lengths $d: E \rightarrow \N_+$ and let $f : 2^V \rightarrow \N_+$  be a a function satisfying:
\item (Symmetric) $f(S) = f(V\backslash S)$ for all $S \subseteq V$
\item (Subadditive) $f(A \cup B) = f(A) + f(B)$ for all $A,B \subseteq V$.
Consider the following integer program, to be labelled $IP$:
\text{min} \sum_{e \in E} d(e) x_e\\
\text{s.t.} \sum_{e\in \delta(S)} x_e &\geq f(S) &\forall S \subseteq V \\
x &\geq 0, \text{ integer}.
\paragraph{Solving $IP$ of Trees}
We first observe that this $IP$ is easy to solve on trees. Indeed let $T$ be a tree, and for every $uv \in E(T)$ let $S^{uv}_u$ denote the set of vertices in connected component of $T-uv$ containing $u$, and define $S^{uv}_v$ similarly. By definition, $\delta(S^{uv}_u) =  \{e\} = \delta(S^{uv}_v)$. We define the following algorithm $\cA$ to solve $IP$ on a tree $T$:
\item For all $uv \in E(T)$ set $x_e = f(S^{uv}_u)$.
\item Return $x$.
To see that $\cA$ solves $IP$ on trees, we will show that $(1)$ the solution returned is feasible, and $(2)$ that every feasible $x$ has necessarily $x_{uv} \geq f(S^{uv}_u)$, implying that the $x$ returned by $\cA$ is optimal.  Let $x$ be the solution returned by $\cA$. 
To see $(1)$, it is immediate from the definition of $f$ that $x \geq 0$. It remains to verify the cut inequalities. Let $S \subseteq V$. Enumerate $\delta(S)$ as $\delta(S) = \{e_1, \dots, e_k \}$, where each $e_i := u_iv_i$ and $u_i \in S$. Let $S_1, \dots, S_\ell$ be the partition of $S$ induced by the connected components of $G-\delta(S)$ contained in $S$.  Now let $D(S_i) = \{ e_j \in \delta(S) : u_j \in S_i \}$ be the set of edges in $\delta(S)$ incident with $S_i$. Notice that the set of $D(S_i)$ partition $\delta(S)$. 
We claim that $\bigcap_{e_j \in D(S_i)} S^{e_j}_{u_j} = S_i.$ If $v \in S_i$ then for all $e_j \in D(S_i)$ there exists a $vu_j$-path that does not use $e_j$, since $v$ and $u_j$ are in the same connected component $S_i$. Thus $v \in \bigcap_{e_j \in D(S_i)}S^{e_j}_{u_j}$. If $v \not\in S_i$ then either $v \in S_{k}$ for $k \neq i$ or $v \in V\backslash S$. In either case, $v$ is connected to any vertex in $S_i$ via a path using some $e_j \in D(S_i)$. But then $v \in S^{e_j}_{v_j} = V \backslash S^{e_j}_{u_j}$. Therefore $v \not\in \bigcap_{e_j \in D(S_i)}S^{e_j}_{u_j}$. Thus the claim holds.
So we have $$S = \bigcup_{i=1}^\ell S_i = \bigcup_{i=1}^\ell \bigcap_{e_j \in D(S_i)}S^{e_j}_{u_j}.$$ Now observe that
f(S) &\leq \sum_{i=1}^\ell f(\bigcap_{e_j \in D(S_i)}S^{e_j}_{u_j}) &\text{by subadditivity} \\
&= \sum_{i=1}^\ell f(V\backslash \bigcap_{e_j \in D(S_i)} S^{e_j}_{u_j}) &\text{by symmetry} \\
&= \sum_{i=1}^\ell f(\bigcup_{e_j\in D(S_i)} V\backslash S^{e_j}_{u_j}). \\
&\leq \sum_{i=1}^\ell \sum_{e_j \in D(S_i)} f(V\backslash S^{e_j}_{u_j}) &\text{by subadditivity} \\
&= \sum_{i=1}^\ell \sum_{e_j \in D(S_i)} f(S^{e_j}_{u_j}) &\text{by symmetry} \\
&= \sum_{e_j \in \delta(S)} f(S^{e_j}_{u_j}) \\
&= \sum_{e_j \i \delta(S)} x_{e_j}.
Hence $x$ satisfies the cut constraint for $S$. Therefore $x$ is feasible and $(1)$ holds.
Now to demonstrate $(2)$, let $uv \in E(T)$. Consider the cut $S^{uv}_u$. We have $\delta(S^{uv}_u) = \{uv\}$ and hence by the cut constraint for $S^{uv}_u$, all feasible $x$ satisfy
$$x_{uv} \geq f(S^{uv}_u).$$
Now the $x$ we construct is tight for all the above, and since $d \geq 0$ we can do no better without violating feasibility. Thus $(2)$ holds and our $x$ is optimal. So we conclude that we can solve $IP$ on trees easily.
\paragraph{An Approximation Algorithm for $IP$}
We now give an algorithm that produces an integral solution to $IP$ for a general metric graph $G$ which approximates the optimal $LP$-relaxation of $IP$ within a factor of $O(\log n)$. Our algorithm will use the following theorem from class:
\begin{theorem} \label{th:metric-tree}
Let $G=(V,E)$ be a graph. Let $d: E \rightarrow \R_+$ be a metric function. Let $\lambda^*_{uv} \geq 0$ be coefficients for all $(u,v) \in V\times V$. There exists a polynomial time algorithm which constructs a weighted tree $T=(V,E)$ such that $d^T(u,v) \geq d(u,v)$ for all $u,v\in V$ and $$\sum_{u,v} \lambda^*_{uv}d^T(u,v) \leq O(\log n) \sum_{u.v} \lambda^*_{uv} d(u,v).$$
\end{theorem}
Consider the algorithm $\cB$:
\item Let $x^*$ be the optimal solution to the linear programming relaxation.
\item Use Theorem \ref{th:metric-tree} with $\lambda^* = x^*$ to obtain a weighted tree $T$.
\item Solve $IP$ on $T$ as discussed above and return the solution $\bar{x}$.
